---
title: "Arc Diagram with Marker Symbols Demo"
---

This is a demo of an arc diagram with marker symbols.

Highcharts Docs: [Data structure](https://www.highcharts.com/docs/chart-and-series-types/arc-diagram#data-structure)

Highcharts Samples: [Arc diagram with custom marker symbol](https://jsfiddle.net/gh/get/library/pure/highcharts/highcharts/tree/master/samples/highcharts/series-arcdiagram/marker-symbol)

::: {.callout-note}
Note the arc diagram series type requires Highcharts version 10.
:::

At this time, the development version of `highcharter` supports HighchartsJS 10.2.0.

[Installation instructions](https://jkunst.com/highcharter/index.html#installation)

# Load packages

```{r}
#| label: load-packages
#| output: false

library(tibble)
library(dplyr)
library(highcharter)
```

# Build data

```{r}
#| label: build-data

df <- tibble(
  c("Brazil", "Portugal", 5),
  c("Brazil", "France", 1),
  c("Brazil", "Spain", 1),
  c("Brazil", "England", 1),
  c("Canada", "Portugal", 1),
  c("Canada", "France", 5),
  c("Canada", "England", 1)
) %>% 
  t() %>% 
  as_tibble() %>% 
  rename(
    from = V1,
    to = V2,
    weight = V3
  ) %>% 
  mutate(
    weight = as.integer(weight)
  )
```

# Set options

```{r}
#| label: set-options

options(
  highcharter.chart = list(
    accessibility = list(
      enabled = TRUE,
      linkedDescription = "Arc diagram chart with the symbol of the data nodes shaped as triangles."
    )
  )
)
```

# Highcharts Version 11 default color palette

```{r}
#| label: version-11-colors

colors_v11 <- c("#2caffe", "#544fc5", "#00e272", "#fe6a35", "#6b8abc", "#d568fb", "#2ee0ca", "#fa4b42", "#feb56a", "#91e8e1")
```

# Arc diagram with marker symbols

```{r}
#| label: arc-diagram-with-marker-symbols

highchartzero() %>% 
  hc_add_dependency("modules/sankey.js") %>%
  hc_add_dependency("modules/arc-diagram.js") %>%
  hc_add_dependency("modules/accessibility.js") %>% 
  hc_colors(colors = colors_v11) %>% 
  hc_title(
    text = "Highcharts Arc Diagram"
  ) %>% 
  hc_subtitle(
    text = "Arc Diagram with marker symbols"
  ) %>% 
  hc_add_series(
    data = df,
    type = "arcdiagram",
    hcaes(from = from, to = to, weight = weight),
    linkWeight = 3,
    marker = list(
      symbol = "triangle",
      lineWidth = 2,
      lineColor = "white"
    ),
    centeredLinks = TRUE,
    dataLabels = list(
      format = "{point.fromNode.name} → {point.toNode.name}",
      nodeFormat = "{point.name}",
      color = "black",
      linkTextPath = list(
        enabled = TRUE
      )
    )
  )
```
